The Forensic Interchange Format - a file format for digital evidence

### 2009-02-21 paper/paper.tex
Added Overlay stream type.

\begin{itemize}
\item A reference starting with {\em file://} refers to an external
file. The external file reference must be sanitised (to remove
.. directory traversal) and rooted at the current directory.

@@

Therefore, the {\em chunk\_size} attribute must be specified. In
addition the {\em compression\_type} attribute MAY be specified. The
attribute should contain an integer corresponding to a suitable Zip
compression scheme (e.g. ZIP\_DEFLATE). If not specified it is assumed
that no compression is used.

The ``target'' stream attribute may be specified multiple times and
refer to external files using the {\em file://} scheme. There can be a
number of overlay segments named ``stream name/overlay.00'' which are
all merged to a single overlay. If more than one overlay is present,
the attribute {\em overlays} MUST be specify how many.

The overlay segment contains a series of lines with comma delimited,
decimal encoded, 64 bit integers representing chunk number, target
offset, target length and target number. Target number is an index
into the targets defined in the attributes (count starts witn zero).
Chunks are then fetched from the specified target and decompressed if
necessary.

A target number of -1 signifies the current file (the zip archive
itself). This can be useful for modifying an existing EWF file to be a
FIF file. Since Zip files are normally read from the end of the file,
but EWF and AFF are both read from the front of the file it may be
possible to append a FIF file to the end of an EWF file without
interfering with the overlayed file. In this case the converted file
can still be used as an EWF file without change, but it can also be
used as a FIF file.

@@

In the above figure a segment is written to the FIF volume which
contains a number of chunks back to back. An overlay stream then uses
direct references to each compressed chunk within the coalesced
segment. Although this technique is valid, it is generally
discouraged since a reorganization of the Zip file might break the
references within the overlay file. This representation also breaks
the appealing simplicity of the standard Image Stream, since it is no
longer possible to simply unzip all the chunks and concatenate them
together to recover the original image.

>>>>

\begin{itemize}
\item A reference starting with {\em file://} refers to an external
file. The external file reference must be sanitised (to remove
.. directory traversal) and rooted at the current directory. A
filename of ``.'' refers to the current FIF volume.

@@

Therefore, the {\em chunk\_size} attribute must be specified. In
addition the {\em compression\_type} attribute MAY be specified. The
attribute should contain an integer corresponding to a suitable Zip
compression scheme (e.g. DEFLATE). If not specified it is assumed
that no compression is used.

The ``target'' stream attribute may be specified multiple times and
refer to external files (See section \ref{target_reference}). There
can be a number of overlay segments named ``stream name/overlay.00''
which are all merged to a single overlay. If more than one overlay is
present, the attribute {\em overlays} MUST be specify how many.

The overlay segment contains a series of lines with comma delimited,
decimal encoded, 64 bit integers representing chunk number, target
offset, target length and target number. Target number is an index
into the targets defined in the attributes (count starts with zero).
Chunks are then fetched from the specified target and decompressed if
necessary.

It is possible to refer to the current file by providing a target of
``file://.''. This can be useful for modifying an existing EWF file to
be a FIF file. Since Zip files are normally read from the end of the
file, but EWF and AFF are both read from the front of the file it may
be possible to append a FIF file to the end of an EWF file without
interfering with the overlayed file. In this case the converted file
can still be used as an EWF file without change, but it can also be
used as a FIF file.

@@

In the above figure a segment is written to the FIF volume which
contains a number of chunks back to back. An overlay stream then uses
direct references to each compressed chunk within the coalesced
segment. The target is then specified as the segment name. Although
this technique is valid, it is generally discouraged since it breaks
the appealing simplicity of the standard Image Stream.  It is no
longer possible to simply unzip all the chunks and concatenate them
together to recover the original image.
